Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-30 sections/results.tex
update text about table iv

To answer this question, timestamps are recorded as three people assess each comment.
Since three people work on their leisure time, there is much variability in the time between each vote.
Therefore, we ignored the time interval between two votes if they are more than 10 minutes apart.

@@

Applying our classification model to all comments results in the proportions shown in Table \ref{tb:percent}.
As the figure shows, the proportion is similar to the result of .

\begin{table}[!t]
\caption{Proportion of classifications when applied to the whole data set.}
\small
\centering
\def\arraystretch{1.2}
\begin{tabular}{ccccccc}
\hline
Class &        over all samples & only training data  \\ \hline
useful &            42.8\%      &      41.8\%         \\
useless &           33.7\%      &      33.1\%         \\
undetermined &      23.5\%      &      25.1\%         \\ \hline
\end{tabular}
\label{tb:percent}
\end{table}

>>>>

To answer this question, timestamps are recorded as three people voted on each comment.
Since three people work in their leisure time, there is much variability in the time between each vote.
Therefore, we ignored the time interval between two votes if they are more than 10 minutes apart.

@@

Applying our classification model to all comments results in the proportions shown in Table \ref{tb:percent}.
As the table shows, the proportions are very similar in both the training dataset and all dataset,
which may suggest that our model will have a similar performance in the real data.

\begin{table}[!t]
\caption{Proportion of classifications when applied to the whole data set.}
\small
\centering
\def\arraystretch{1.2}
\begin{tabular}{ccccccc}
\hline
Classification & over all samples & only training data  \\ \hline
useful &            42.8\%      &      41.8\%         \\
useless &           33.7\%      &      33.1\%         \\
undetermined &      23.5\%      &      25.1\%         \\ \hline
\end{tabular}
\label{tb:percent}
\end{table}
